---
title: "Biostatistical Computing, PHC 6068"
author: "Zhiguang Huo (Caleb)"
date: "Monday September 11, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: null
subtitle: R graphics
---

Outline: what you expect to learn
===
- plot basics
    - scattered plot
    - margins
    - histogram and heatmap
- ggplot2
- lattice



Plotting in R
===
R is powerful to visualize your data.

- plot(): a generic plotting function
    - points(): add points to the plot.
    - lines(), abline(): add lines
    - text(): add text 
    - legend(): add legend
- hist(): histogram
- image(), heatmap(): heatmaps
- boxplot(): boxplot
- curve(): any function curve
- contour(): contour plot



scattered plot
===
```{r}
n <- 80
set.seed(32611)
x <- sort(runif(n, min = 0, max=2*pi))
y <- sin(x) + rnorm(n, mean = 0, sd = 0.2)
plot(x,y)
```


Type
===

- "p": for points
- "l": for lines
- "b" for both,
- "o" for both ‘overplotted’,
- "n" for no plotting.

---

```{r}
plot(x,y, type="p") ## default is "p"
```

---

```{r}
plot(x,y, type="l")
```

---

```{r}
plot(x,y, type="b")
```

---

```{r}
plot(x,y, type="o")
```

---

```{r}
plot(x,y, type="n")
```


Labels
===

- main: title
- xlab: x labels
- ylab: y labels

```{r}
plot(x,y, main="sin function with Gaussian noise") # default xlab and ylab are the variable names of the arguments
```


---

```{r}
plot(x,y, main="sin function with Gaussian noise", 
     xlab="x axis", ylab="y axis") 
```


Text and Symbol Size
===
- cex: number indicating the amount by which plotting text and symbols should be scaled relative to the default. 1=default, 1.5 is 50% larger, 0.5 is 50% smaller, etc.
- cex.axis	magnification of axis annotation relative to cex
- cex.lab	magnification of x and y labels relative to cex
- cex.main	magnification of titles relative to cex
- cex.sub	magnification of subtitles relative to cex

--- 
```{r}
plot(x,y, main="sin function with Gaussian noise", 
     xlab="x axis", ylab="y axis", 
     cex=2, cex.axis=2, cex.lab=2, cex.main=2, cex.sub=2) 
```



Point type
===
- pch is an argument for point typs
```{r}
plot(1:25,1:25,pch=1:25)
```

---

- use pch = 19
```{r}
plot(x,y, pch=19) 
```


Lines
===
- lty:	line type. see the chart below.

- lwd	line width relative to the default (default=1). 2 is twice as wide.
