---
title: "HW sparse clustering"
author: "Name: (E.g. Caleb Huo)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE) ## prevent read in string data to factors.
```


In this question we will apply the sparse $k$-means algorithm and the sparse hierarchical algorithm on the iris data.
The Iris data is directly available in R. 
There are `r nrow(iris)` samples and `r nrow(iris[,1:4])` features in the iris data.
The fifth column of the iris data is species.
Below is the head of the iris data.

```{r}
head(iris)
```

In order to demonstrate the effectiveness of feature selection of the sparse $k$-means algorithm and the sparse hierarchical algorithm,
we also added $p_2 = 10$ noise features.
Then the noise data is combined with the original data. 
Then the combined data (iris2) is further scaled to mean 0 and sd 1 for each feature.
You only need to start with iris2 as the input data throughout this HW.
Below is how to prepare iris2 as well as iris_label.

```{r}
n <- nrow(iris)
p2 <- 10
set.seed(32611)
iris_noise <- matrix(rnorm(n*p2), ncol=p2)
iris_label <- iris$Species

iris2 <- cbind(iris[,1:4], iris_noise)
iris2 <- scale(iris2)
iris2 <- as.matrix(iris2)
```

### Part 1, apply the sparse $k$-means algorithm.
Apply sparse $k$-means algorithm to iris2 data to cluster the samples.
Fix the number of clusters to be K=3. 
Fix the tuning parameter wbounds $wbounds = 1.9$.
Draw the feature selection plot similarly to <https://caleb-huo.github.io/teaching/2018SPRING/lectures/sparseClustering1.html#(29)>.
Also preform PCA to iris2, visualize the data using the first two principal components, label each sample with the same color according their species.
Also add appropriate legend to the result.


```{r}
```


### Part 2, apply the sparse hierarchical clustering algorithm.
Apply sparse hierarchical clustering algorithm to iris2 data to cluster the samples.
Fix the tuning parameter wbounds $wbounds = 1.9$ with complete linkage.
Draw the hierarchical tree structure and feature selection plot similarly to <https://caleb-huo.github.io/teaching/2018SPRING/lectures/sparseClustering2.html#(16)>.
Also draw the hierarchical tree structure with each sample colored according their species.
Also add appropriate legend to the result.


```{r}
```


## Note:

### Homework should be uploaded to courseweb <http://elearning.ufl.edu>:
1. If you know how to generate knitted html files by Rmd, please submit a html file (only html). Rename the file name as: hw6_Lastname_Firstname.html.
2. Otherwise, you can submit your homework in any format.

### If you generate a figure, please write appropriate figure title, labels, legend if necessary.

### If your code is not intuitive, please write comments to make the code readible.


