%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
%\usepackage{color,hyperref}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{caption}

%\pagestyle{fancy}
%\fancyhf{}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}


\name{Zhiguang (Caleb) Huo} % Your name


\address{(352)-294-5929 \\ \url{zhuo@ufl.edu}} % Your phone number and email
\address{\url{https://caleb-huo.github.io}} % Your phone number and email
\address{(352)-294-5929 \\ \url{zhuo@ufl.edu}} % Your phone number and email
\address{2004 Mowry Road, 5th Floor CTRB, P.O. Box 117450, Gainesville, FL 32611-7450} % Your address

\begin{document}

\pagestyle{plain}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\footnotetext{Last modified: \today}

\begin{rSection}{Education}
\href{http://www.pitt.edu}{\textbf{University of Pittsburgh}}, \hfill{Pittsburgh, PA, US}
\begin{itemize}[noitemsep,topsep=0pt]
\item Ph.D. in
        \href{http://www.publichealth.pitt.edu/biostatistics}
             {Biostatistics},
              \hfill{\em April 2017}
	\begin{itemize}
        \item Dissertation:  \emph{Statistical integrative omics methods for disease subtype discovery}
        \item GPA: \emph{3.93/4.00}
        \item Advisors:
              \href{http://www.pitt.edu/~ctseng/}
                   {George C. Tseng, ScD} and
              \href{http://www.publichealth.pitt.edu/home/directory/yong-seok-park/}
                   {Yong Seok Park, PhD}
	\end{itemize}
	\item M.S. in
        \href{http://www.physicsandastronomy.pitt.edu}
             {Physics}, \hfill {\em Apr 2012}              
	\begin{itemize}
	\item {\emph{GPA: 3.86/4.00}}
	\end{itemize}
\end{itemize}

\href{http://www.hit.edu.cn} {\textbf{Harbin Institute of Technology}},
\hfill{Harbin, Heilongjiang, China}
\begin{itemize}[noitemsep,topsep=0pt]
\item B.S. in
        \href{http://physics.hit.edu.cn/}
             {Physics}, \hfill {\em June 2011} 
        \begin{itemize}
        \item GPA: \emph{90.43/100}
        \end{itemize}

\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interest}
My research interest lies in the intersection between statistical methodology and its applications to genomics and bioinformatics.	
I am particularly interested in genomic data integration, models and variable selection in high-dimensional data, graphical models, Bayesian methods, optimization and statistical computing. 
I have collaborated with biologists in the fields of cancer, psychiatry and aging, analyzing a broad range of genomic data. 
These experiences motivate me to develop methodology and software that are practical, user-friendly and easy to use.
\end{rSection}

\begin{rSection}{Professional Experience}
\begin{itemize}[noitemsep,topsep=0pt]

\item Assistant Professor
        \hfill {\em July 2017 $\sim$ Now} 
        \begin{itemize}
        \item Department of Biostatistics, University of Florida
        \end{itemize}
\end{itemize}
\end{rSection}

%------------------------------------------------
\begin{rSection}{Publications on statistical methodology}
$^\dagger$: co-first author; $^*$: corresponding author; \underline{\mbox{ }\mbox{ }\mbox{ }\mbox{ }}: student paper.

\textbf{2022}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item
\underline{Lingsong Meng}, Dorina Avram, George Tseng, {\bf Zhiguang Huo}$^*$.  (2022)
Outcome-guided Sparse K-means for Disease Subtype Discovery via Integrating Phenotypic Data with High-dimensional Transcriptomic Data.
\emph{Journal of the Royal Statistical Society: Series C (Applied Statistics)}, 71(2), 352-375.

\end{enumerate}


\textbf{2021}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item
\underline{Haocheng Ding}, \underline{Lingsong Meng}, Andrew C. Liu, Michelle L. Gumz, Andrew J. Bryant, Colleen A. Mcclung, George Tseng, Karyn A. Esser, {\bf Zhiguang Huo}$^*$.  (2021)
Likelihood-based Tests for Detecting Circadian Rhythmicity and Differential Circadian Patterns in Transcriptomic Applications. 
\emph{Briefings in Bioinformatics} Nov 5;22(6):bbab224.

\item  
Chi Song, Shih-Chi Su, {\bf Zhiguang Huo}, Suleyman Vural, James E. Galvin, and Lun-Ching Chang. (2021) 
HCMMCNVs: Hierarchical Clustering Mixture Model of Copy Number Variants Detection us-ing Whole Exome Sequencing in Cancer Genomes
\emph{Bioinformatics}, 37(18), 3026-3028.

\end{enumerate}

\textbf{2020}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item  {\bf  Zhiguang Huo}, Shaowu Tang, Yongseok Park, George Tseng. (2020) 
P-value evaluation, variability index and biomarker categorization for adaptively weighted Fisher's meta-analysis method in omics applications. 
\emph{Bioinformatics} 36(2), 524-532.

\item {\bf  Zhiguang Huo*}, Li Zhu, Tianzhou Ma, Hongcheng Liu, Song Han, Daiqing Liao, Jinying Zhao and George Tseng*.  (2020)
Two-way Horizontal and Vertical Omics Integration for Disease Subtype Discovery. \emph{Statistics in Bioscience} 12, 1-22.

\end{enumerate}

\textbf{2019}
\begin{enumerate}[noitemsep,topsep=0pt,resume]

\item 
{\bf Zhiguang Huo}, Chi Song$^*$, George C. Tseng$^*$. 
Bayesian latent hierarchical model for transcriptomic meta-analysis to detect biomarkers with clustered meta-patterns of differential expression signals. \emph{The Annals of Applied Statistics} 13, no. 1 (2019): 340-366. (An earlier version won ASA Biometrics Section JSM Travel Award 2018)

\item Li Zhu, {\bf  Zhiguang Huo}, Tianzhou Ma, George Tseng. (2019)
Bayesian indicator variable selection to incorporate multi-layer overlapping group structure in multi-omics applications. 
\emph{The Annals of Applied Statistics} 13(4), 2611-2636. 
(An earlier version won ENAR distinguished student paper award 2018)

\end{enumerate}


\textbf{2018}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item Tianzhou Ma$^\dagger$, {\bf  Zhiguang Huo$^\dagger$}, Anche Kuo$^\dagger$, Li Zhu, Fang Zhou, Xiangrui Zeng, Chien-Wei Lin, Silvia Liu, Lin Wang, Tanbin Rahman, Lun-Ching Chang, Sunghwan Kim, Jia Li, Yongseok Park, Chi Song, Steffi Oesterreich, Etienne Sibille and George C. Tseng. 
MetaOmics - Comprehensive Analysis Pipeline and Web-based Software Suite for Transcriptomic Meta-Analysis. \emph{Bioinformatics} 35, no. 9 (2018): 1597-1599. 

\item Kelly Cahill$^\dagger$, {\bf  Zhiguang Huo$^\dagger$}, George Tseng, Ryan W. Logan*, Marianne L. Seney*.
Improved identification of concordant and discordant gene expression signatures using an updated rank-rank hypergeometric overlap approach. \emph{Scientific Reports} 8.1 (2018): 9588.

\item 
Wang, Kai Wen, Xiangrui Zeng, Xiaodan Liang, {\bf Zhiguang Huo}, Eric P. Xing, and Min Xu (2018). Image-derived generative modeling of pseudo-macromolecular structures-towards the statistical assessment of Electron CryoTomography template matching. \emph{The British Machine Vision Conference}

\end{enumerate}

\textbf{2017}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item {\bf Zhiguang Huo}, George C. Tseng. 
    Integrative Sparse $K$-means with overlapping group lasso in genomic applications for disease subtype discovery.
    \emph{The Annals of Applied Statistics}, 11(2) (2017): 1011-1039.

\item 
SungHwan Kim, Dongwan Kang, {\bf Zhiguang Huo}, Yongseok Park, and George C. Tseng. 
Meta-analytic principal component analysis in integrative omics application. 
\emph{Bioinformatics} 34, no. 8 (2017): 1321-1328.

\end{enumerate}

\textbf{2016}
\begin{enumerate}[noitemsep,topsep=0pt,resume]

 \item  {\bf Zhiguang Huo}, Ying Ding, Silvia Liu, Steffi Oesterreich, and George Tseng. Meta-Analytic Framework for Sparse $K$-Means to Identify Disease Subtypes in Multiple Transcriptomic Studies. \emph{Journal of the American Statistical Association},  111, no. 513 (2016): 27-42.

\item 
Zhu, Li, Ying Ding, Cho-Yi Chen, Lin Wang,  {\bf Zhiguang Huo}, SungHwan Kim, Christos Sotiriou, Steffi Oesterreich, and George C. Tseng. MetaDCN: meta-analysis framework for differential co-expression network detection with an application in breast cancer. \emph{Bioinformatics} 33, no. 8 (2016): 1121-1129.
\end{enumerate}

\textbf{2015 and Before}
\begin{enumerate}[noitemsep,topsep=0pt,resume]
    \item Silvia Liu, Wei-Hsiang Tsai, Ying Ding, Rui Chen, Zhou Fang, {\bf Zhiguang Huo}, SungHwan Kim, Tianzhou Ma, Ting-Yu Chang, Nolan Michael Priedigkeit, Adrian V. Lee, Jianhua Luo, Hsei-Wei Wang, I-Fang Chung, George C. Tseng. (2015).
Comprehensive evaluation of fusion transcript detection algorithms and a meta-caller to combine top performing methods in paired-end RNA-seq data.
\emph{Nucleic Acids Research}, 44(5), e47-e47. 

\item SungHwan Kim,  {\bf Zhiguang Huo}, YongSeok Park and George Tseng.  (2015) MetaOmics: transcriptomic meta-analysis methods for biomarker detection, pathway analysis and other exploratory purposes. Book chapter in Integrating omics data: statistical and computational methods. Edited by George C. Tseng, Debashis Ghosh, Xianghong Jasmine Zhou. \emph{Cambridge University Press}. Page 39-67.

    \item Xingbin Wang, Dongwan Kang, Kui Shen, Chi Song, Shuya Lu, Lunching Chang, Serena G. Liao, {\bf Zhiguang Huo}, Naftali Kaminski, Etienne Sibille, Yan Lin, Jia Li and George C. Tseng. (2012) A Suite of R Packages for Quality Control, Differentially Expressed Gene and Enriched Pathway Detection in Microarray Meta-analysis. \emph{Bioinformatics}, 28:2534-2536.

\end{enumerate}


\end{rSection}

\begin{rSection}{Publications on biomedical applications}
$^\dagger$: co-first author; $^*$: corresponding author; \underline{\mbox{ }\mbox{ }\mbox{ }\mbox{ }}: student paper.

\textbf{2022}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item
Tengfei Bian$^\dagger$, \underline{Haocheng Ding}$^\dagger$, Yuzhi Wang, Qi Hu, Jin Koh, Sixue Chen, Naomi Fujioka, F. Zahra Aly, Junxuan Lu$^*$, {\bf Zhiguang Huo}$^*$ and Chengguo Xing$^*$.
Suppressing the activation of protein kinase A as a DNA damage-independent mechanistic lead for dihydromethysticin (DHM) prophylaxis of NNK-induced lung carcinogenesis.
\emph{Carcinogenesis} (Accepted)

\item
Jessica A. Peterson, Larissa J. Strath, Chavier Laffitte Nodarse , Asha Rani, {\bf Zhiguang Huo}, \underline{Lingsong Meng}, James Cole, Thomas C. Foster, Roger B. Fillingim, Yenisel Cruz-Almeida. 
Accelerated Epigenetic Aging Mediates the Association between Pain Impact and Predicted Brain Age Difference in Middle to Older Age Individuals with Knee Pain.  
\emph{Epigenetics} (Accepted)

\item  
Johnson AJ, Buchanan T, Laffitte Nodarse C, Valdes Hernandez PA, {\bf Huo Z}, Cole JH, Buford TW, Fillingim RB, Cruz-Almeida Y.
Cross-Sectional Brain-Predicted Age Differences in Community-Dwelling Middle-Aged and Older Adults with High Impact Knee Pain. 
\emph{J Pain Res} (Accepted)

\item Epigenetic Age Predictors in Community-Dwelling Adults with High Impact Knee Pain.
Cruz-Almeida, Yenisel; Johnson, Alisa; \underline{Meng, Lingsong}; Rani, Asha; Sinha, Puja; Yoder, Sean; {\bf Huo, Zhiguang}; Foster, Thomas; Fillingim, Roger.
\emph{Molecular Pain} (Accepted)

\item
Tengfei Bian, Yuzhi Wang, Jordy Botello, Qi Hu, Yunhan Jiang, Adriana Zingone, \underline{Haocheng Ding}, Yougen Wu, F. Aly, Ramzi Salloum, Graham Warren, {\bf Zhiguang Huo}, Brid Ryan, Lingtao Jin, and Chengguo Xing. 
LKB1 phosphorylation and deactivation in lung cancer by NNAL, a metabolite of tobacco-specific carcinogen, in an isomer-dependent manner.
\emph{Oncogene} (Accepted)

\item
Edwin N. Aroke, \underline{Lingsong Meng}, {\bf Zhiguang Huo}, Yenisel Cruz-Almeida, Burel Goodin.
Differential DNA Methylation in Black and White Individuals with Chronic Low Back Pain Enrich Different Genomic Pathways. 
\emph{Neurobiology of Pain}, 11, 100086.

\item
Larissa Jane Strath; \underline{Lingsong Meng}; Asha Rani; Puja Sinha; Alisa Johnson; Ricarrdo Marioni; {\bf Zhiguang Huo}; Thomas Foster; Roger Fillingim; Yenisel Cruz-Almeida. 
Accelerated Epigenetic Aging Mediates the Association between Vitamin D Levels and Knee Pain in Community-Dwelling Individuals. 
\emph{Journal of nutrition, health \& aging}, 26(4), 318-323.

\item
Helena Palma-Gudiel, Lei Yu, {\bf Zhiguang Huo}, Jingyun Yang, Tongjun Gu, Cheng Gao, Philip L. De Jager, Peng Jin, David A. Bennett, Jinying Zhao.
Fine-mapping and replication of EWAS loci harboring putative epigenetic alterations associated with AD neuropathology in a large collection of human brain tissue samples. \emph{Alzheimer's \& Dementia} (Accepted)

\item
Yuzhi Wang, Tengfei Bian, Lina Song, Yunhan Jiang, {\bf Zhiguang Huo}, Ramzi Salloum, Graham Warren, Frederic J. Kaye, Naomi Fujioka, Lingtao Jin, Chengguo Xing.
Reducing chemotherapy-induced DNA damage via nAChR-mediated redox reprograming - a new mechanism for SCLC chemoresistance boosted by nicotine.
\emph{Cancers}, 14(9), 2272.

\item
Santanu Hati$^\dagger$, Qi Hu$^\dagger$, {\bf Zhiguang Huo}, Junxuan Lu, Chengguo Xing. 
In vivo structure-activity relationship of dihydromethysticin in reducing NNK-induced lung DNA damage against lung carcinogenesis.
\emph{ChemMedChem} (Accepted)

\item
Qi Hu,Pedro Corral, Stephen S. Hecht, F. Zahra Aly,  {\bf Zhiguang Huo}, Chengguo Xing.
Characterization of adductomic totality of NNK, (R)-NNAL, and (S)-NNAL in A/J mice, and their correlations with distinct lung carcinogenicity. 
\emph{Carcinogenesis}, 43(2), 170-181.

\item
Johnson, Alisa; Laffitte Nodarse, Chavier; Peraza, Julio; Valdes-Hernandez, Pedro; Montesino-Goicolea, Soamy; {\bf Huo, Zhiguang}; Fillingim, Roger; Cruz-Almeida, Yenisel. 
Psychological profiles in adults with knee OA-related pain: A replication study.
\emph{Therapeutic Advances in Musculoskeletal Disease} (Accepted)

\item  
Brendan M. Gabriel, Ali Altintas, Richard Tjörnhammar, Laura Sardon-Puig, Jonathon A.B. Smith, Xiping Zhang, Astrid L. Basse, Rhianna C. Laker, Carles Canto, Hui Gao, Jonas T. Treebak, Antonio Zorzano, {\bf Zhiguang Huo}, Mikael Rydén, Karyn A. Esser, Nicolas J. Pillon, Romain Barrès, Anna Krook, Juleen R. Zierath. 
Disrupted Circadian Oscillations in Type 2 Diabetes are Linked to Altered Rhythmic Mitochondrial Metabolism in Skeletal Muscle
\emph{Science Advances}, 7(43), eabi9654.

\item  
Fullwood, Dottington; Gomez, Rebecca; {\bf Huo, Zhiguang}; Cardoso, Josue; Bartley, Emily; Booker, Staja; Powell-Roach, Keesha; Johnson, Alisa; Sibille, Kimberly; Sotolongo, Adriana; Goodin, Burel; Staud, Roland; Redden, David; Fillingim, Roger; Terry, Ellen. 
A mediation appraisal of catastrophizing, pain-related outcomes, and race in adults with knee osteoarthritis. 
\emph{The Journal of Pain}, 22(11), 1452-1466.

\end{enumerate}


\textbf{2021}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item  {\bf Zhiguang Huo}, Brinda K. Rana, Jeremy A. Elman, Ruocheng Dong, Corinne D. Engelman, Sterling C. Johnson, Michael J. Lyons, Carol E. Franz, William S. Kremen, Jinying Zhao.
Metabolic profiling of cognitive aging in midlife.
\emph{Frontier in Aging Neuroscience} 12 (2020): 397.

\item
Aaron R Waddell, Iqbal Mahmud, \underline{Haocheng Ding}, {\bf Zhiguang Huo}, Daiqing Liao. 
Pharmacological inhibition of CBP/p300 blocks estrogen receptor alpha (ERa) function through suppressing enhancer H3K27 acetylation in luminal breast cancer.
\emph{Cancers} 13, no. 11 (2021): 2799.

\item
Theodore Drashansky, Eric Helm, Nina Curkovic, Jaimee Cooper, Xiaoping Luo, \underline{Lingsong Meng}, William Collins, Benjamin Keselowsky, Derek Sant'Angelo, {\bf Zhiguang Huo}, Liang Zhou, Dorina Avram.
BCL11B is positioned upstream of PLZF and ROR$\gamma$t to control thymic development of mucosal-associated invariant T cells and MAIT17 program.
\emph{iScience}  24, no. 4 (2021): 102307.

\item  
Yang Shen, Wei Wang, Mehari Endale, Lauren J Francey, Rachel L Harold, David W Hammers, {\bf Zhiguang Huo}, Carrie L Partch, ProfileJohn Hogenesch, Zhao-Hui Wu, Andrew C Liu.
NF-kB modifies the mammalian circadian clock through interaction with the core clock protein BMAL1.
\emph{PLOS Genetics} 17, no. 11 (2021): e1009933.


\item 
 Pedro Valdes-Hernandez; Soamy Montesino-Goicolea; Lorraine Hoyos; Eric C Porges; {\bf Zhiguang Huo}, Natalie C Ebner; Adam J Woods; Ronald Cohen; Joseph L Riley III; Roger B Filligim; Yenisel Cruz-Almeida. 
 Resting State Functional Connectivity Patterns are Associated with Chronic Pain Duration in Community-Dwelling Older Adults. 
\emph{Pain Report},  6, no. 4 (2021).


\item
Lei Yu, {\bf Zhiguang Huo}, Jingyun Yang, Patricia A. Boyle, Julie A. Schneider, David A. Bennett, Jinying Zhao.
Human brain and blood N-glycome profiling in AD/ADRD.
\emph{Frontiers in Aging Neuroscience} (2021) 13, 765259. 

\item
Guanhong Miao, Ying Zhang, {\bf Zhiguang Huo}, Wenjie Zeng, Jianhui Zhu, Jason G. Umans, Gert Wohlgemuth, Diego Pedrosa, Brian DeFelice, Shelley A. Cole, Elisa T. Lee, Barbara V. Howard, Oliver Fiehn, Jinying Zhao.
Longitudinal Plasma Lipidome and Risk for Type 2 Diabetes in a Large Sample of American Indians with Normal Fasting Glucose: The Strong Heart Family Study. 
\emph{Diabetes Care}  44, no. 12 (2021): 2664-2672.


\item
Welch, Nicole; Singh, Shashi; Kumar, Avinash; Dhruba, Saugato; Mishra, Saurabh; Sekar, Jinendiran; Bellar, Annette; Attaway, Amy; Chelluboyina, Aruna; Willard, Belinda; Li, Ling; {\bf Huo, Zhiguang}; Esser, Karyn; Karnik, Sadhashiva; Longworth, Michelle; Shah, Yatrik; Davuluri, Gangarao; Pal, Ranadip; Dasarathy, Srinivasan.
Integrated multiomics analysis identifies molecular landscape perturbations during hyperammonemia in skeletal muscle and myotubes. 
\emph{Journal of Biological Chemistry}, 297, no. 3 (2021).


\item  
Nicholas J. Saner, Matthew JC Lee, Jujiao Kuang, Nathan W. Pitchford, Gregory D. Roach, Andrew Garnham, Amanda J. Genders; Tanner Stokes; Elizabeth A Schroder; {\bf Zhiguang Huo}; Esser A Karyn; Stuart M Phillips; David J Bishop; Jonathan D Bartlett.
Exercise mitigates sleep-loss-induced changes in glucose tolerance, mitochondrial function, sarcoplasmic protein synthesis, and diurnal rhythms.
\emph{Molecular Metabolism} 43 (2021): 101110.

\item  
Burcu F. Darsta, {\bf Zhiguang Huo}, Erin M. Jonaitis, Rebecca L. Koscik, Lindsay R. Clarkc, Qiongshi Lu, William S. Kremen, Carol E. Franz, Brinda Rana, Michael J. Lyons, Kirk J. Hogan, Jinying Zhao, Sterling C. Johnsonc, Corinne D. Engelman.
Metabolites Associated with Early Cognitive Changes Implicated in Alzheimer's Disease.
\emph{Journal of Alzheimer Disease} JAD 79, no. 3 (2021): 1041-1054.


\item  Joseph Collins, {\bf Zhiguang Huo}, Danxin Wang, 
ESR1 ChIP-Seq Identifies Distinct Ligand-Free ESR1 Genomic Binding Sites in Human Hepatocytes and Liver Tissue.
\emph{International journal of molecular sciences} 22, no. 3 (2021): 1461.

\end{enumerate}


\textbf{2020}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item  {\bf Zhiguang Huo}, Lei Yu, Jingyun Yang, Yun Zhu,  David A. Bennett, Jinying Zhao. (2020)
Brain and blood metabolome for Alzheimer's dementia: Findings from a targeted metabolomics analysis.
\emph{Neurobiology of aging}  86, 123-133.

\item
Ryan W. Logan, Angela R. Ozburn, Rachel N. Arey, Kyle D. Ketchesin, Alicia Winquist, Andrew Crain, Brian T. D. Tobe, Darius Becker-Krail, Matthew B. Jarpe, Xiangning Xue, Wei Zong, {\bf Zhiguang Huo}, Puja K. Parekh, Xiyu Zhu, Ethan Fitzgerald, Hui Zhang, Jeffrey Oliver-Smith, Lauren M. DePoy, Mariah Hildebrand, Evan Y. Snyder, George C. Tseng, and Colleen A. McClung. 
Valproate reverses mania-like behaviors in mice via preferential targeting of HDAC2.
\emph{Molecular Psychiatry} (2020): 1-19.

\item 
Marianne Seney, William Paden, Kelly Barko, Rachel Puralewski, Kelly Cahill, {\bf Zhiguang Huo}, Micah Shelton, George Tseng, and Ryan Logan
(2020)
Sex differences in adult mood and in stress-induced transcriptional coherence across mesocorticolimbic circuitry.
\emph{Translational Psychiatry}  10(1), pp.1-14.

\item
Nader Shaikh, Judith M Martin, Alejandro Hoberman, Megan Skae, Linette Milkovich, Christi McElheny, Robert W Hickey, Diana Kearney, Massoud Majd, Eglal Shalaby-Rana, George Tseng, John F Alcorn, Jay Kolls, Marcia Kurs-Lasky, William Horne, {\bf Zhiguang Huo}, Timothy R Shope.  (2020)
Biomarkers that differentiate false positive urinalyses from true urinary tract infection. 
\emph{Pediatric Nephrology}  35(2), 321-329..



\item
Ali Zarrinpar,  Ting-Yuan D Cheng, {\bf Zhiguang Huo}. (2020)
What Can We Learn About Drug Safety and Other Effects in the Era of Electronic Health Records and Big Data That We Would Not Be Able to Learn from Classic Epidemiology?
\emph{Journal of Surgical Research} 246, 599-604.

\item 
Saunjoo L. Yoon, Oliver Grundmann, Joseph J. Williams, Samuel S. Wu, Christiaan Leeuwenburgh, {\bf Zhiguang Huo}, and Thomas J. George Jr. (2020)
Differential response to targeted acupuncture by gender in patients with gastrointestinal cancer cachexia: secondary analysis of a randomized controlled trial.
\emph{Acupuncture in Medicine}  38(1), 53-60.

\item
Kristin Curry Greenwood,  Jennifer Kirwin, {\bf Zhiguang Huo}. (2020)
Design and Implementation of the Health Professions Simulation Assessment, a Tool to Assess Students' Perceptions of Simulation Experiences. \emph{Journal of Acute Care Physical Therapy}, 11(2), 70-78.


 
\item
Yonghan He, Sajid Khan, {\bf Zhiguang Huo}, Dongwen Lv, Xuan Zhang, Xingui Liu, Yaxia Yuan, Robert Hromas, Mingjiang Xu, Guangrong Zheng, Daohong Zhou. (2020)
Proteolysis targeting chimeras (PROTACs) are emerging therapeutics for hematologic malignancies.
\emph{Journal of Hematology \& Oncology}, 13(1), 1-24.

\item  
Soamy Montesino-Goicolea, Pedro A Valdes-Hernandez,  Lorraine Hoyos, Adam J. Woods, Ronald Cohen,  {\bf Zhiguang Huo}, Joseph L. Riley III, Eric C. Porges, Roger B. Fillingim, Yenisel Cruz-Almeida. (2020)
Cortical thickness mediates the association between self-reported pain and sleep quality in community-dwelling older adults. 
\emph{Journal of Pain Research}, 13:2389-2400.


\item
Soamy Montesino-Goicolea, Puja Sinha; {\bf Zhiguang Huo}; Asha Rani; Thomas Foster; Yenisel Cruz-Almeida. (2020)
Enrichment of Genomic Pathways Based on Differential DNA Methylation Profiles Associated With Chronic Musculoskeletal Pain in Older Adults: An Exploratory Study
\emph{Molecular Pain}, 16, 1744806920966902.

\item  
Tengfei Bian, Pedro Corral, Yuzhi Wang, Jordy Botello, Rick Kingston, Tyler Daniels, Ramzi Salloum, Edward Johnston, {\bf Zhiguang Huo}, Andrew Liu,  Junxuan Lu, Chengguo Xing. (2020)
Kava as a clinical nutrient: promises and challenges.
\emph{Nutrients}, 12(10), 3044.




\end{enumerate}


\textbf{2019}
\begin{enumerate}[noitemsep,topsep=0pt,resume]

\item 
{\bf Zhiguang Huo}, Yun Zhu, Lei Yu, Jingyun Yang, Philip De Jager, David A. Bennett, Jinying Zhao.
 DNA methylation variability in Alzheimer's Disease. \emph{Neurobiology of aging} 76 (2019): 35-44.

\item Song Han$^*$, {\bf Zhiguang Huo}$^*$,  Kathy Nguyen,  Fanchao Zhu, Patrick W Underwood, Kari Basso, Thomas George, and Steven Hughes. (2019)
The Proteome of Pancreatic Cancer-Derived Exosomes Reveals Signatures Rich in Key Signaling Pathways. \emph{Proteomics}, 19(13), 1800394.

\item Marianne L. Seney, Kelly Cahill, John F. Enwright III, Ryan W. Logan, {\bf  Zhiguang Huo}, Wei Zong, George Tseng, and Colleen A. McClung. (2019) Diurnal rhythms in gene expression in the prefrontal cortex in schizophrenia. \emph{Nature Communications} 10, no. 1 (2019): 1-11.

\item Li Zhu, {\bf  Zhiguang Huo}, Tianzhou Ma, George Tseng. (2019)
Bayesian indicator variable selection to incorporate multi-layer overlapping group structure in multi-omics applications. 
\emph{The Annals of Applied Statistics} 13(4), 2611-2636. 
(An earlier version won ENAR distinguished student paper award 2018)

\item  
Nader Shaikh, Judith M Martin, Alejandro Hoberman, Megan Skae, Linette Milkovich, Andrew Nowalk, Christi McElheny, Robert W Hickey, Diana Kearney, Massoud Majd, Eglal Shalaby-Rana, George Tseng, John F Alcorn, Jay Kolls, Marcia Kurs-Lasky, {\bf Zhiguang Huo}, William Horne, Greg Lockhart, Hans Pohl, Timothy R Shope. 
(2019)
Host and Bacterial Markers that Differ in Children with Cystitis and Pyelonephritis. \emph{The Journal of pediatrics} , 209, 146-153.

\item Yenisel Cruz-Almeida, Puja Sinha, Asha Rani, {\bf Zhiguang Huo}, Roger Benton Fillingim, Thomas C Foster. (2019)
Epigenetic Aging is Associated with Clinical and Experimental Pain in Community-Dwelling Older Adults.
\emph{Molecular Pain}, 15 (2019): 1744806919871819.

\item 
Theodore Drashansky$^\dagger$, Eric  Helm$^\dagger$, {\bf Zhiguang Huo}, Upasana Parthasarathy,  Ashley Zuniga, Jonathan Cho, Zhiwei Xu,  Mohammad Uddin,  Kyle Lorentsen, Safiehkhatoon Moshkani, Liang Zhou, Nina Curkovic, Preet Kumar,  Xiaoping Luo, Dorina Avram. (2020)
Bcl11b prevents fatal autoimmunity by promoting Treg cell program and constraining innate lineages in Treg cells. 
\emph{Science Advances}, 5(8), eaaw0480.


\end{enumerate}

\textbf{2018}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item Marianne Seney,  {\bf Zhiguang Huo},  Kelly Cahill, Leon French, Rachel Puralewski, Joyce Zhang, Ryan W. Logan, George Tseng, David A Lewis, Etienne Sibille. Opposite molecular signatures of depression in men and women. \emph{Biological Psychiatry}  84, no. 1 (2018): 18-27.

\item 
John Enwright, {\bf Zhiguang Huo}, Dominique Arion, John P. Corradi, George Tseng, and David A. Lewis. 
Transcriptome alterations of prefrontal cortical parvalbumin neurons in schizophrenia. 
\emph{Molecular psychiatry} 23, no. 7 (2018): 1606.

\item 
Cynthia R. Johnson, Kimberly Brown, Susan Hyman, Maria M. Brooks, Courtney Aponte, Lynne Levato, Brianna Schmidt,
Victoria Evans, {\bf Zhiguang Huo},  Roxanna Bendixen, Heather Eng, Theresa Sax, Tristram Smith.
Parent Training for Feeding Problems in Children with Autism Spectrum Disorder: Initial Randomized Trial. \emph{Journal of pediatric psychology} 44, no. 2 (2018): 164-175.

\end{enumerate}

\textbf{2017}
\begin{enumerate}[noitemsep,topsep=0pt, resume]

\item  
Dominique Arion, {\bf Zhiguang Huo}, John F. Enwright, John P. Corradi, George Tseng, and David A. Lewis. Transcriptome alterations in prefrontal pyramidal cells distinguish schizophrenia from bipolar and major depressive disorders. \emph{Biological psychiatry} 82, no. 8 (2017): 594-600.

\end{enumerate}



\textbf{2016 and before}
\begin{enumerate}[noitemsep,topsep=0pt,resume]

    \item Tiffany A. Katz, Serena G. Liao, Vincent J. Palmieri, Robert K. Dearth, Thushangi Pathiraja, {\bf Zhiguang Huo}, Patricia Shaw, Sarah Small, Nancy E. Davidson, David G. Peters, George C. Tseng, Steffi Oesterreich, Adrian V. Lee. Targeted DNA Methylation Screen in the Mouse Mammary Genome Reveals a Parity-Induced Hypermethylation of IGF1R That Persists Long after Parturition. \emph{Cancer Prevention Research} 8, no. 10 (2015): 1000-1009.

    \item Yan P. Yu, Silvia Liu, {\bf Zhiguang Huo}, Amantha Martin, Joel B. Nelson, George C. Tseng and Jian-Hua Luo. (2015) Genomic copy number variations in the genomes of leukocytes predict prostate cancer clinical outcomes. \emph{PloS one}, 10(8):e0135982.

\end{enumerate}


\end{rSection}

\begin{rSection}{Award}
\textbf{Academic Awards}
\begin{itemize}[noitemsep,topsep=0pt]

\item  Colledge of Public Health and Health Professional, University of Florida \hfill Sep 2020
\begin{itemize}[noitemsep,topsep=0pt]
\item Dean's citation award
\end{itemize}

\item  Department of Biostatistics, University of Florida \hfill March 2019
\begin{itemize}[noitemsep,topsep=0pt]
\item Outstanding Teacher
\end{itemize}
\end{itemize}


\textbf{Student Awards}
\begin{itemize}[noitemsep,topsep=0pt]
\item  Delta Omega Membership \hfill April 2017
\item American Statistics Association (ASA) Pittsburgh chapter  \hfill March 2016
\begin{itemize}[noitemsep,topsep=0pt]
\item Student of the year
\end{itemize}
\item Department of Physics, Harbin Institute of Technology \hfill May 2009
\begin{itemize}[noitemsep,topsep=0pt]
\item National Scholarship of P.R. China. \\(Awarded to the top 2 students in my Bachelors degree.)
\end{itemize}
\end{itemize}


\textbf{Travel Awards} 

\begin{itemize}[noitemsep,topsep=0pt]
\item 2018 ASA Biometrics Section JSM Travel Award, Vancouver, BC, Canada. \hfill Aug 2018
\end{itemize}

\begin{itemize}[noitemsep,topsep=0pt]
\item Objective Bayes meeting 2017 travel award, Austin, TX. \hfill Dec 2017
\end{itemize}

\begin{itemize}[noitemsep,topsep=0pt]
\item SAMSI, Research Triangle Park, NC.	
\begin{itemize}[noitemsep,topsep=0pt]
\item {Interface of Statistics and Optimization} \hfill Feb 2017
\item {Optimization Summer School} \hfill Aug 2016
\item {Epigenetics Workshop} \hfill Mar 2015
\item {Beyond Bioinformatics Workshop} \hfill June 2014
\end{itemize}

\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Teaching Experience }

\textbf{Lecturer, University of Florida}
\begin{itemize}[noitemsep,topsep=0pt]
\item PHC6937 - Introduction to Biostatistical Computing	 \hfill Feb 2022
\item PHC6937 - Frontiers in Biostatistics \hfill Feb 2020, Feb 2018
\item PHC6068 - Biostatistical computing \hfill Fall 2017 $\sim$ Fall 2021
\end{itemize}


\textbf{Lecturer, University of Pittsburgh}
\begin{itemize}[noitemsep,topsep=0pt]
\item BIOST2094 - Advanced R Computing -- (with Tianzhou Ma) \hfill Spring 2017
\item BIOST2025 - Special Studies in Bayesian Data Analysis  \hfill Fall 2016
\begin{itemize}[noitemsep,topsep=0pt]
\item{(with George Tseng, Tianzhou Ma and Li Zhu)}
\end{itemize}
\end{itemize}


\textbf{Guest Lecturer, University of Pittsburgh}
\begin{itemize}[noitemsep,topsep=0pt]
\item BIOST2055 - Introductory high-throughput genomic data analysis I: \\data mining and applications \hfill Mar 2016
\begin{itemize}[noitemsep,topsep=0pt]
\item{Differential and isoform analysis of RNA-seq data}
\end{itemize}
\item BIOST2078 - Introductory high-throughput genomic data analysis II: \\theories and algorithms  \hfill Dec 2015
\begin{itemize}[noitemsep,topsep=0pt]
\item{Reproducible research and parallel computing in R}
\end{itemize}
\item BIOST2078 - Introductory high-throughput genomic data analysis II: \\theories and algorithms  \hfill Dec 2014
\begin{itemize}[noitemsep,topsep=0pt]
\item{Reproducible research}
\end{itemize}
\end{itemize}

\textbf{Teaching Assistant, University of Pittsburgh}
\begin{itemize}[noitemsep,topsep=0pt]
\item BIOST 2078 - Introductory high-throughput genomic data analysis II: \\theories and algorithms \hfill {Fall 2014}
\item PHYS 0212 - Introduction to Laboratory Physics \hfill {Spring 2012}
\item PHYS 0212 - Introduction to Laboratory Physics \hfill {Fall 2011}
\end{itemize}

\end{rSection}

\begin{rSection}{Presentations}
\textbf{Invited Oral Presentation}

\begin{itemize}[noitemsep,topsep=0pt]

\item  International Chinese Statistical Association conference, Gainesville, FL  \hfill {June 2022}
\begin{itemize}[noitemsep,topsep=0pt]
\item{A Bayesian Framework for Outcome-guided Clusterings via Integrating \\Clinical Data with High-dimensional Transcriptomic Data.}
\end{itemize}

\item  International Chinese Statistical Association conference (virtual), Houston, TX  \hfill {Dec 2020}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Outcome-guided Sparse K-means for Disease Subtype Discovery via Integrating \\Phenotypic Data with High-dimensional Transcriptomic Data}
\end{itemize}

\item  Division of Biostatistics,  Albert Einstein College of Medicine, Bronx, NY  \hfill {Oct 2019}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Statistical methods on omics data integration for disease subtype discovery.}
\end{itemize}

\item  Rush Alzheimer's Disease Center ROSMAP Investigator's Meeting, Chicago, IL  \hfill {April 2019}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Brain and blood metabolome for Alzheimer's dementia.}
\end{itemize}

\item  Department of Physiology and Functional Genomics at UF, Gainesville, FL  \hfill {October 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Statistical methods on omics data meta-analysis and integration, for \\
disease subtype discovery and differential expression analysis.}
\end{itemize}

\item  Joint Statistical Meetings, Vancouver, BC, Canada  \hfill {August 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Bayesian meta-analysis for biomarkers of meta-patterns.}
\end{itemize}

\item  International Chinese Statistical Association conference, New Brunswick, NJ  \hfill {June 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Two-way Horizontal and Vertical Omics Integration for Disease Subtype Discovery.}
\end{itemize}


\item  Rush Alzheimer's Disease Center ROSMAP Investigator's Meeting, Chicago, IL  \hfill {May 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Identifying variably methylated regions (VMRs) associated with AD.}
\end{itemize}

\item  International Indian Statistical Association conference, Gainesville, FL \hfill {May 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Two-way Horizontal and Vertical Omics Integration for Disease Subtype Discovery.}
\end{itemize}

\item  Department of Biostatistics, University of Florida, Gainesville, FL \hfill {Feb 2017}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic and integrative framework for sparse $K$-means to\\ identify disease subtypes.}
\end{itemize}


\end{itemize}


\textbf{Contributed Poster and Oral Presentation}

\begin{itemize}[noitemsep,topsep=0pt]


\item  Poster, ENAR converence, Atlanta, GA \hfill {Mar 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{p-value evaluation, variability index and biomarker categorization for \\adaptively
weighted Fisher's meta-analysis method in omics applications}
\end{itemize}


\item  Poster, 2018 UF Stats Winter Workshop, University of Florida, Gainesville, FL \hfill {Jan 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Bayesian latent hierarchical model for transcriptomic meta-analysis to detect\\ biomarkers with clustered meta-patterns of differential expression signals}
\end{itemize}

\item  Poster, Objective Bayes meeting 2017, University of Texas, Austin, TX \hfill {Dec 2017}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Bayesian latent hierarchical model for transcriptomic meta-analysis to detect\\ biomarkers with clustered meta-patterns of differential expression signals}
\end{itemize}

\item  Poster, Dean's Day's competition, GSPH, University of Pittsburgh \hfill {April 2017}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Circadian rhythms of gene expression in the human prefrontal cortex \\reveal distinct pattern between schizophrenia and control subjects}
\end{itemize}

\item Oral Presentation, ENAR, Washington, DC \hfill {Mar 2017}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Bayesian latent hierarchical model for transcriptomic meta-analysis to detect\\ biomarkers with clustered meta-patterns of differential expression signals.}
\end{itemize}




\item Poster, SAMSI optimization summer school,  Research Triangle Park, NC  \hfill {Aug 2016}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Integrative Sparse $K$-means for disease subtype discovery using \\multi-level omics data.}
\end{itemize}

\item Poster, Pittsburgh ASA banquet, Pittsburgh, PA \hfill {Mar 2016}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Integrative Sparse $K$-means for disease subtype discovery using \\multi-level omics data.}
\end{itemize}

\item Department of Biostatistics, University of Pittsburgh  \hfill Nov 2015
\begin{itemize}[noitemsep,topsep=0pt]
\item{How to use Latex to make slides}
\end{itemize}

\item Oral Presentation, JSM, Seattle, WA \hfill {Aug 2015}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic framework for sparse $K$-means to identify disease\\ subtypes in multiple transcriptomic studies.}
\end{itemize}

\item Poster, Pittsburgh ASA banquet, Pittsburgh, PA \hfill {Apr 2015}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic framework for sparse $K$-means to identify disease\\ subtypes in multiple transcriptomic studies.}
\end{itemize}

\item Oral Presentation, ENAR Conference, Miami, FL \hfill {Mar 2015}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic framework for sparse $K$-means to identify disease\\ subtypes in multiple transcriptomic studies.}
\end{itemize}

\item Poster, Dean's Day's competition, GSPH, University of Pittsburgh \hfill {Mar 2015}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Discover and Characterize Invasive Lobular Breast Carcinoma Subtypes.}
\end{itemize}

\item Oral Presentation, ENAR Conference, Baltimore, MA \hfill {Mar 2014}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic framework for sparse $K$-means to identify disease\\ subtypes in multiple transcriptomic studies.}
\end{itemize}

\item Poster, Dean's Day's competition, GSPH, University of Pittsburgh \hfill {Mar 2014}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Meta-analytic framework for sparse $K$-means to identify disease \\ subtypes in multiple transcriptomic studies.}
\end{itemize}
\end{itemize}



\end{rSection}

%\begin{rSection}{References}
%\textbf{George C. Tseng}
%\begin{itemize}[noitemsep,topsep=0pt]
%\item[] Professor \hfill {Phone: 412-624-5318}\\
%Department of Biostatistics (primary appointment) \hfill{E-mail: ctseng@pitt.edu }\\
%Department of Human Genetics \\
%Department of Computational \& Systems Biology 
%\\
%University of Pittsburgh
%\end{itemize}

%\textbf{Yong Seok Park}
%\begin{itemize}[noitemsep,topsep=0pt]
%\item[] Assistant Professor \hfill {Phone: 412-624-3028}\\
%Department of Biostatistics \hfill{E-mail: yongpark@pitt.edu}\\
%University of Pittsburgh
%\end{itemize}

%\textbf{David A. Lewis, MD}
%\begin{itemize}[noitemsep,topsep=0pt]
%\item[] Distinguished Professor of Psychiatry and Neuroscience, \\
%Thomas Detre Professor of Academic Psychiatry, Chair  
%\hfill {Phone: 412-246-6010}\\
%Department of Psychiatry \hfill{E-mail: lewisda@upmc.edu}\\
%University of Pittsburgh
%\end{itemize}

%\end{rSection}

\begin{rSection}{Conference service}

\begin{itemize}[noitemsep,topsep=0pt]

\item  ICSA, Gainesville, FL  \hfill {June 2022}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Chair for Session Recent advancement in statistical learning methods for high-dimensional biomedical data.}
\end{itemize}


\item  ICSA, New Brunswick, NJ  \hfill {June 2018}
\begin{itemize}[noitemsep,topsep=0pt]
\item{Chair for Session New developments in microbiome sequencing data modeling and analysis.}
\item{Chair for Session Modern Statistical Development for Biomedical Big data.}
\end{itemize}


\end{itemize}

\end{rSection}


\begin{rSection}{Reviewer service}

\begin{table}[htp]
\begin{center}
\begin{tabular}{l c }
\hline
\hline
\bf{Statistical journal} & Count \\
\hline
Journal of the American Statistical Association & 1 \\
Journal of the Royal Statistical Society Series C & 1 \\
Biometrics & 3 \\
Bioinformatics & 3 \\
BMC Bioinformatics & 1 \\
Statistics in Bioscience & 1 \\
Journal of Statistical Research & 1 \\
Journal of Data Science & 1 \\
\hline
\hline
\bf{Biological journal} &  \\
\hline
Nucleic Acids Research & 1 \\
American Journal of Epidemiology & 1 \\
PLOS ONE & 3 \\
Scientific Reports & 2 \\
Journal of Alzheimer's Disease & 4 \\
Alzheimer's \& Dementia Journal & 1 \\
Frontiers Immunology & 1 \\
BMC Medicine & 1 \\
\hline
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%


\end{rSection}

\begin{rSection}{Department/College service}
\begin{itemize}[noitemsep,topsep=0pt]

\item Member of PHHP Faculty Council
        \hfill {\em June 2020 $\sim$ now} 
        \begin{itemize}
        \item College of Public Health and Health Professions, University of Florida
        \end{itemize}

\item Member of PhD Qualifying Exam commitee 
        \hfill {\em Jan 2018 $\sim$ Aug 2022} 
        \begin{itemize}
        \item Department of Biostatistics, University of Florida
        \end{itemize}

\item Director of the Biostatistics Consulting Lab
        \hfill {\em Sep 2017 $\sim$ June 2019} 
        \begin{itemize}
        \item Department of Biostatistics, University of Florida
        \end{itemize}


\end{itemize}
\end{rSection}


\begin{rSection}{Ph.D. advising}

\begin{table}[htp]
\caption*{\textbf{Committee Chair}}
\begin{center}
\begin{tabular}{l l l l}
\hline
\hline
Name & Department & Graduation Time & First position \\
\hline
Haocheng Ding & Biotatistics, UF & Active &  \\
Lingsong Meng & Biotatistics, UF & Active &  \\
Yutao Zhang & Biotatistics, UF & Active &  \\
\hline
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%


\begin{table}[htp]
\caption*{\textbf{Committee Member}}
\begin{center}
\begin{tabular}{l l l l}
\hline
\hline
Name & Department & Graduation Time & First position \\
\hline
Shaojun Zhang & Statistics, UF & July 2018 & 84.51$^\circ$ \\
Satyajit Ghosh & Statistics, UF & July 2018 & postdoc at Rutgers University \\
Jalalli Peyman & Statistics, UF & April 2019 & Wells Fargo \\
Minji Lee & Statistics, UF & June 2020 &postdoc at Columbia University\\
Zhongkai Wang &  Biostatistics, UF & July 2020 & Eli Lilly \\
Tamal Ghosh & Statistics, UF & July 2020 & \\
Roy Samrat & Statistics, UF & July 2020 & \\
Suman Bhattacharya & Statistics, UF & March 2021 & \\
Ruoyang Zhang & Statistics, UF & May 2021 & \\
Eric Helm &  Anatomy and Cell Biology, UF & Nov 2021 & \\
Sourav Mukherjee & Statistics, UF & July 2022 & \\
Jiayuan Zhou & Statistics, UF & July 2022 & \\
Nilanjana Chakraborty & Statistics, UF & July 2022 & \\
Srijata Samanta & Statistics, UF & July 2022 & \\
Fatmah Alamoudi & Nursing, UF & Active & \\
Tingting Hou & Biostatistics, UF & Active & \\
Xiaoru Dong & Biostatistics, UF & Active & \\
Dongyuan Wu & Biostatistics, UF & Active & \\
Seungjun Ahn & Biostatistics, UF & Active & \\
Sagnik Halder & Statistics, UF & Active & \\
\hline
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

\end{rSection}


\begin{rSection}{Membership}
\begin{itemize}[noitemsep,topsep=0pt]
\item Member of International Chinese Statistical Association
        \hfill {\em Mar 2015 $\sim$ Now} 
\item Member of Eastern North American Region International Biometric Society
        \hfill {\em Oct 2013 $\sim$ Now} 
\item Member of American Statistical Association
        \hfill {\em Nov 2013 $\sim$ Now} 
\end{itemize}
\end{rSection}


\begin{rSection}{Hobbies}
Running, skiing, other endurance activities.

\begin{table}[htp]
\caption*{Running Record}
\begin{center}
\begin{tabular}{l l l l}
\hline
\hline
Name & Location  & Date \\
\hline
%HITS half ironman & Sarasota, FL & 01/09/2022 \\
Horrible Hundred (Century ride) & Clermont, FL &  {11/21/2021} \\
Five Points of Life Half Marathon & Gainesville, FL &  {02/16/2020} \\
HITS half ironman & Sarasota, FL & 01/05/2020 \\
Santa Fe Century (Century ride)  & Gainesville, FL & 10/26/2019 \\
Las Olas International Triathlon & Fort Lauderdale, FL &  {03/10/2019} \\
Five Points of Life Half Marathon & Gainesville, FL &  {02/16/2019} \\
The Southernmost Marathon & Key West, FL &  {10/06/2018}\\
Dick's Sporting Goods Pittsburgh Half Marathon & Pittsburgh, PA &  {05/06/2018}\\
Five Points of Life Race Marathon & Gainesville, FL&   {02/18/2018}\\
Bank of America Chicago Marathon & Chicago, IL&   {10/09/2016}\\
First National Bank Pittsburgh Triathlon (Sprint) & Pittsburgh, PA &   {08/14/2016}\\
Dick's Sporting Goods Pittsburgh Marathon & Pittsburgh, PA&   {05/01/2016} \\
First National Bank Pittsburgh Triathlon & Pittsburgh, PA &  {08/09/2015}\\
Dick's Sporting Goods Pittsburgh Marathon & {Pittsburgh, PA} &  {05/03/2015}\\
Dick's Sporting Goods Pittsburgh Marathon & {Pittsburgh, PA} &    {{05/04/2014}}\\
Dick's Sporting Goods Pittsburgh Marathon & {Pittsburgh, PA} &   {05/05/2013}\\
\hline
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%


\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
