%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
%\usepackage{color,hyperref}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}

%\pagestyle{fancy}
%\fancyhf{}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}


\name{Zhiguang (Caleb) Huo} % Your name


\address{(352)-294-5929 \\ \url{zhuo@ufl.edu}} % Your phone number and email
\address{\url{https://caleb-huo.github.io}} % Your phone number and email
\address{(352)-294-5929 \\ \url{zhuo@ufl.edu}} % Your phone number and email
\address{2004 Mowry Road, 5th Floor CTRB, P.O. Box 117450, Gainesville, FL 32611-7450} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\footnotetext{Last modified: \today}


%------------------------------------------------
\begin{rSection}{Submitted}

$^\dagger$: co-first author; $^*$: corresponding author; \underline{\mbox{ }\mbox{ }\mbox{ }\mbox{ }}: student paper.

\textbf{Submitted}
\begin{enumerate}[noitemsep,topsep=0pt]

\item
\underline{Lingsong Meng}, Dorina Avram, George Tseng, {\bf Zhiguang Huo}$^*$.
Outcome-guided Sparse K-means for Disease Subtype Discovery via Integrating Phenotypic Data with High-dimensional Transcriptomic Data.
(Submitted to Journal of the Royal Statistical Society: Series C (Applied Statistics))


\item  {\bf Zhiguang Huo}, Brinda K. Rana, Jeremy A. Elman, Ruocheng Dong, Corinne D. Engelman, Sterling C. Johnson, Michael J. Lyons, Carol E. Franz, William S. Kremen, Jinying Zhao.
Metabolic profiling of cognitive aging in midlife.
(Submitted to Frontier in aging neuroscience)


\item
Dorina Avram, Upasana Parthasarathy, Ashley Zuniga, Zhiwei Xu, Mu Yu, Kevin Luque-Sanchez, Xiaoping Luo, Jonathan Cho, Eric Helm, Theodore Drashansky, Zhen He, Christian Jobin, Mariola Edelmann, Hamsa Thayele Purayil, Yehia Daaka, Kartika Venugopal, Olga Guryanova, Daiqing Liao, Jian Li, Sarah Glover, Marcus Muehlbauer, {\bf Zhiguang Huo}, Alexander Kwiatkowski, Benjamin G Keselowsky, Thomas George, Daohong Zhou, Yaxia Yuan, and Liang Zhou. 
Deficiency in HECTD3 promotes increased colonic tumorigenesis and inflammation. 
(Submitted to Gastroenterology)

\item  Daiqing Liao, Iqbal Mahmud, Guimei Tian, {\bf Zhiguang Huo}, Jia Wang, Jessica Lewis, Aaron Waddell, Lisa Zhao, Jian-Liang Li, Timothy Garrett, and Yehia Daaka. 
DAXX drives de novo lipogenesis and is a novel target for cancer therapy. 
(Submitted to Cell Press journals)


\item  Joseph Collins, Zhiguang Huo, Danxin Wang, 
Estrogen receptor alpha (ESR1) ChIP-Seq identifies distinct ligand-free ESR1 genomic binding sites in human hepatocytes and liver tissue.
(Submitted to Human Molecular Genetics)


\item  
Burcu F. Darsta, {\bf Zhiguang Huo}, Erin M. Jonaitis, Rebecca L. Koscik, Lindsay R. Clarkc, Qiongshi Lu, William S. Kremen, Carol E. Franz, Brinda Rana, Michael J. Lyons, Kirk J. Hogan, Jinying Zhao, Sterling C. Johnsonc, Corinne D. Engelman.
Metabolites associated with early cognitive changes implicated in Alzheimer?s disease.
(Submitted to Journal of Alzheimer Disease)

\item  
Soamy Montesino-Goicolea, Pedro A Valdes-Hernandez,  Lorraine Hoyos, Adam J. Woods, Ronald Cohen,  {\bf Zhiguang Huo}, Joseph L. Riley III, Eric C. Porges, Roger B. Fillingim
Cortical thickness mediates the association between self-reported pain and sleep quality in community-dwelling older adults. 
(Submitted to Experimental Gerontology)

\item  
Brendan M. Gabriel, Ali Alt?nta?, Richard Tjörnhammar, Laura Sardon-Puig, Jonathon A.B. Smith, Xiping Zhang, Astrid L. Basse, Rhianna C. Laker, Carles Canto, Hui Gao, Jonas T. Treebak, Antonio Zorzano, {\bf Zhiguang Huo}, Mikael Rydén, Karyn A. Esser, Nicolas J. Pillon, Romain Barrès, Anna Krook, Juleen R. Zierath. 
Disrupted circadian core-clock oscillations in Type 2 Diabetes
attenuate rhythmic mitochondrial metabolism.
(Submitted to Nature Metabolism)


\item  Pedro A Valdes-Hernandez, Soamy Montesino-Goicolea, Natalie Ebner, Eric S Porges, Adam J Woods,
Ronald A Cohen, 
{\bf Zhiguang Huo},
Joseph Leo Riley,
Roger Benton Fillingim,
Yenisel Cruz-Almeida.
Resting State Functional Connectivity Patterns are Associated with Chronic Pain Duration in Community-Dwelling Older Adults. 
(Submitted)

\item
Lauren M. Decker, {\bf Zhiguang Huo}, \underline{Haocheng Ding}, Michael S. Simpson, Stephanie L. Woelfel, Beth A. Smith.
Just be Confident!: An analysis of factors related to increases in student confidence in the acute care setting.
(Submitted to Journal of Physical Therapy Education)

\item
Hongcheng Liu, Hung Yi Lee, {\bf Zhiguang Huo}. 
High-Dimensional Learning with Linear Constraints. 
(Submitted to Mathematics of Operations Research)


\end{enumerate}


\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
