---
title: "HW example"
author: "Caleb"
date: "Due: 11:59 pm, Aug 29th, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
result <- NULL
result$firstName <- "your first name"
result$lastName <- "your last name"
result$GatorLinkID <- "zhuo" ## i.e. prefix for your uf email address
result$teammate <- NULL ## default is NULL, otherwise specify your teammate's name
```

## Question A
#### 1. Calculate $\sum_{i=1}^{1000} \frac{1}{i^2}$

```{r}
## Your code

result$A1 <- NULL ## replace NULL with your answer (by replacing NULL with the variable containing your answer)
```

#### 2. Fibonacci number follows the following recurrence relation:
$F_n = F_{n-1} + F_{n-2}$.
Given the seed value $F_1 = 1$ and $F_2 = 1$, what is $F_{100}$?

```{r}
## Your code

result$A2 <- NULL ## replace NULL with your answer (by replacing NULL with the variable containing your answer)
```

## Question B
#### 1. In R base package, there is cars' data. data(cars), plot speed (x axis) vs dist (y axis).
```{r}
## Your code
```

## Question C

In R base package, there is mtcars' data. data(mtcars)

#### 1. Fit a linear model: treat mpg as response variable and cyl, disp, hp and drat as predictors.
```{r}
## Your code
```
#### 2. Find the p-value for cyl.
```{r}
## Your code

result$C2 <- NULL ## replace NULL with your answer (by replacing NULL with the variable containing your answer)
```


## Note:
#### Save your result as Rdata. So Auto grading can be performed.
The chunk of code will verify that the Rdata contains your name, GatorLinkID, answers to all questions
```{r}
verify <- function(result){
  ## first verify your basic information, if not, error will come up.
  if(is.null(result$firstName)){
    stop("firstName is missing")
  } else {
    cat("Name:", result$firstName, " ")
  }
  if(is.null(result$lastName)){
    stop("lastName is missing")
  } else {
    cat(result$lastName, "\n")
  }
  if(is.null(result$GatorLinkID)){
    stop("GatorLinkID is missing")
  } else {
    cat("GatorLinkID:", result$GatorLinkID, "\n")
  }
  if(is.null(result$teammate)){
    cat("You have no teammate\n")
  } else {
    cat("Your teammate is", result$teammate, "\n")
  }

  ## second verify if you have provide an answer, if not, warning will come up.
  completeAnswer <- TRUE
  if(is.null(result$A1)) {
    warning("Question A1 is answered")
    completeAnswer <- FALSE
  }
  if(is.null(result$A2)) {
    warning("Question A2 is answered")
    completeAnswer <- FALSE
  }
  if(is.null(result$C2)) {
    warning("Question C2 is answered")
    completeAnswer <- FALSE
  }
  if(completeAnswer) cat("Congratulations! All questions are answered!\n")

}

verify(result) ## verify your result
save(result, file="hw1_Lastname_Firstname.Rdata") ## save your result
```



### Homework should be uploaded to courseweb:
1. Save your compiled result as html/pdf file. Rename the file name as: hw1_lastname_firstname.html or hw1_lastname_firstname.pdf.
2. RMD file is not required.
3. Save your result as Rdata and name it as hw1_lastname_firstname.Rdata.
4. (Optional): you can zip 1 (html/pdf) and 3 (Rdata) as hw1_lastname_firstname.zip.
5. You can upload to courseweb (1 and 3) or 4.

### If you generate a figure, please write appropriate figure title, labels, legend if necessary.

### If your code is not intuitive, please write comments to make the code readible.


