---
title: "Biostatistical Computing, PHC 6068"
author: "Zhiguang Huo (Caleb)"
date: "Monday September 13, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: null
subtitle: Matrix operation
---

Outlines
===
- Basic Matrix operations
- Data reshape
- SVD and PCA

Create a matrix
===
- an example from ?matrix
```{r}
mdat <- matrix(c(1,2,3, 11,12,13), nrow = 2, ncol = 3, byrow = FALSE,
               dimnames = list(c("row1", "row2"),
                               c("C.1", "C.2", "C.3")))
mdat
```

- an alternative way
```{r}
mdat <- c(1,2,3, 11,12,13)
dim(mdat) <- c(2,3)
dimnames(mdat) <- list(c("row1", "row2"), c("C.1", "C.2", "C.3"))
mdat
```

appending a column  or a row to a matrix
===
```{r}
dim(mdat)
```
- appending a column
```{r}
mat2 <- cbind(mdat, c(3,4))
dim(mat2)
```

- appending a row
```{r}
mat3 <- rbind(mdat, c(2,5,8))
dim(mat3)
```


subset of a matrix
===
- by numeric index
```{r}
mdat[1,1]
mdat[1,1:2]
mdat[1,]
mdat[1,-1]
mdat[,]
```

---

- by names
```{r}
dimnames(mdat); rownames(mdat); colnames(mdat)
mdat["row1", "C.1"]
mdat["row2", c("C.2", "C.3")]
mdat["row1",-2] ## mixed usage
```

element-wise Multiplication by a Scalar/Vector/Matrix
===
- by a scalar
```{r}
mdat * 3
```

- by a **column** vector
```{r}
mdat * c(1,2)
```


- by a matrix of the same dimension
```{r}
mdat * matrix(1:6,nrow=2,ncol=3)
```


Addition/Subtraction by a Scalar/Vector/Matrix
===
- by a scalar
```{r}
mdat + 3
```

- by a **column** vector
```{r}
mdat - c(1,2)
```


- by a matrix of the same dimension
```{r}
mdat + matrix(1:6,nrow=2,ncol=3)
```



