---
title: "Biostatistical Computing, PHC 6068"
author: "Zhiguang Huo (Caleb)"
date: "Monday September 13, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: null
subtitle: Matrix operation
---

Outlines
===
- Basic Matrix operations
- Data reshape
- SVD and PCA

Create a matrix
===
- an example from ?matrix
```{r}
mdat <- matrix(c(1,2,3, 11,12,13), nrow = 2, ncol = 3, byrow = FALSE,
               dimnames = list(c("row1", "row2"),
                               c("C.1", "C.2", "C.3")))
mdat
```

- an alternative way
```{r}
mdat <- c(1,2,3, 11,12,13)
dim(mdat) <- c(2,3)
dimnames(mdat) <- list(c("row1", "row2"), c("C.1", "C.2", "C.3"))
mdat
```

appending a column  or a row to a matrix
===
```{r}
dim(mdat)
```
- appending a column
```{r}
mat2 <- cbind(mdat, c(3,4))
dim(mat2)
```

- appending a row
```{r}
mat3 <- rbind(mdat, c(2,5,8))
dim(mat3)
```


subset of a matrix
===
- by numeric index
```{r}
mdat[1,1]
mdat[1,1:2]
mdat[1,]
mdat[1,-1]
mdat[,]
```

---

- by names
```{r}
dimnames(mdat); rownames(mdat); colnames(mdat)
mdat["row1", "C.1"]
mdat["row2", c("C.2", "C.3")]
mdat["row1",-2] ## mixed usage
```

element-wise Multiplication by a Scalar/Vector/Matrix
===
- by a scalar
```{r}
mdat * 3
```

- by a **column** vector
```{r}
mdat * c(1,2)
```


- by a matrix of the same dimension
```{r}
mdat * matrix(1:6,nrow=2,ncol=3)
```


Addition/Subtraction by a Scalar/Vector/Matrix
===
- by a scalar
```{r}
mdat + 3
```

- by a **column** vector
```{r}
mdat - c(1,2)
```


- by a matrix of the same dimension
```{r}
mdat + matrix(1:6,nrow=2,ncol=3)
```



Matrix Multiplication
===
- %*%

```{r}
mat1 <- matrix(1:6,nrow=2,ncol=3)
mat1

mat2 <- matrix(1:6,nrow=3,ncol=2)
mat2

mat1 %*% mat2

mat2 %*% mat1
```

Transponse of a Matrix
===
- t
```{r}
mat1 <- matrix(1:6,nrow=2,ncol=3)
mat1
t(mat1)
```

Diagonal Matrix
===
- diag()
    - if input is a square matrix, return the diagnal element.
    - if input is a vector, return a diagnal matrix.
```{r}
S <- matrix(1:9,3,3)
S
diag(S)
diag(diag(S))
```


Inverse of a Matrix
===
```{r}
S <- matrix(c(4,4,-2,2,6,2,2,8,4),3,3)
SI <- solve(S)
SI
S %*% SI
SI %*% S

```

Determinant of a Matrix
===
- det()
```{r}
S <- matrix(c(4,4,-2,2,6,2,2,8,4),3,3)
det(S)
```

- rank (rank function has been implemented for the purpose of rank of a vector)
- To get the rank of a matrix:
```{r}
S <- matrix(c(4,4,-2,2,6,2,2,8,4),3,3)
QR <- qr(S)
QR$rank
```

Column and Row Means
===
- row mean
```{r}
S <- matrix(c(4,4,-2,2,6,2,2,8,4),3,3)
apply(S,1,mean)
rowMeans(S)
```

- column mean
```{r}
S <- matrix(c(4,4,-2,2,6,2,2,8,4),3,3)
apply(S,2,mean)
colMeans(S)
```
