---
title: "Biostatistical Computing, PHC 6068"
subtitle: "Overview"
author: Zhiguang Huo (Caleb)
date: "Monday August 21, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: null
---

Why biostatisticians learn to program
===

- **Job:** Industry, academic, collaboration...
- **Independence:** otherwise, you rely on someone else giving you exactly the right tool
- **Honesty:** otherwise, you end up distorting your problem to match the tools you have
- **Clarity:** often, turning your ideas into something a machine can do refines your thinking
- **Fun:** these were the best of times (the worst of times)


Basic description of this class
===

- Lecturer Zhiguang Huo (Caleb)
- TAs: 
- Lecture times:
    * Monday: 12:50-2:45pm, [MAEB](https://campusmap.ufl.edu/#/index/0720), Room 0234 
    * Wednesday: 1:55-2:45pm, [MAEB](https://campusmap.ufl.edu/#/index/0720), Room 0234 
- Office hours:
    * Tuesdays 3-5pm, [CTRB](https://campusmap.ufl.edu/#/index/1375), Room 5230
- Course Website: 

[https://caleb-huo.github.io/teaching/2017FALL/biostatisticalComputing.html](https://caleb-huo.github.io/teaching/2017FALL/biostatisticalComputing.html)

- [elearning](http://elearning.ufl.edu/): used to collect submissions, and keep track of grades
- [Syllabus](https://caleb-huo.github.io/teaching/2017FALL/PHC6068_Biostatistical_Computing_Syllabus.pdf): will be explained in the following slides.

---

- No programming knowledge assumed
- Some statistics knowledge assumed 
    * PHC 6092: Biostatistical Theory 
    * PHC 6050: Statistical Methods for Health Sciences Research I
    * PHC 6051: Biostatistical Methods II
- Focus almost entirely on R 
- Class will be cumulative, so keep up with the material and assignments!

---

Contents of this class
===

```{r echo = FALSE, results = 'asis'}
suppressWarnings(library(knitr))
Requirement <- paste("Week",1:15)
topic1 <- "data structure, subsetting, regex, Rmarkdown"
topic2 <- "functions, HiPerGator (when to use?)"
topic3 <- "Basic plot, ggplot2, lattice function, spline smoothing, vectorized calculation?"
topic4 <- "matrix operations, sweep, apply, SVD, PCA (implementation)"
topic5 <- "linear model, AIC/BIC, lasso, ridge regression"
topic6 <- "GLM, Random intercept model, GEE"
topic7 <- "optimization: gradient decent, coordinate decent, Newton's method"
topic8 <- "mid-term exam"
topic9 <- "Simulating random variables?"
topic10 <- "simulation: size and power of a statistical test or method, compare competing tests, asymptotics?"
topic11 <- "object-oriented programming: S3, S4"
topic12 <- "Building R packages, devtools, calling c++"
topic13 <- "Bootstrap, permutation, cross validation, compare competing models"
topic14 <- "Monte Carlo integration, importance sampling, Gibbs sampling, Metropolis-Hasting"
topic15 <- "Multivariate optimization: LDA, SVM, tree-based methods, random forests?"

Topics <- c(topic1,topic2,topic3,topic4,topic5,topic6,topic7,topic8,topic9,
            topic10,topic11,topic12,topic13,topic14,topic15)
ContentTable <- data.frame(Requirement, Topics)
kable(ContentTable)
```

Assignment
===

```{r echo = FALSE, results = 'asis'}
#suppressWarnings(library(knitr))
Requirement <- c("Homework1", "Homework2", "Homework3", "Homework4", "Mid-term exam",
                 "Homework5", "Homework6", "Homework7", "Final exam", "Final project")
distributeDate <- character(length(Requirement))
dueDate <- character(length(Requirement))
points <- c("5%", "5%", "5%", "5%", "20%", "5%", "5%", "5%", "30%", "10%")
gradeTable <- data.frame(Requirement, distributeDate, dueDate, points)
kable(gradeTable, caption = "grading criteria")
```

Exams
===
- Mid-term exam
- Final exam


Final project
===
- Wrap up a R package (with one of these options)
    * S3/S4 class
    * calling c++
    * make nice vignette
- Complete documentation of all your functions.
- Apply R package to real data or synthetic data.
- Report using R markdown, include how you used your own package.


R, R Studio, R Markdown
===

- R is a programming language for statistical computing
- R Studio is an integrated development environment for R programming  
- R Markdown is a markup language for combining R code with text

All 3 are free, and all 3 will be used extensively in this course

(survey, demo)


Things you should have done, by the end of this week
===

- Install R Studio on your laptop
- Get comfortable with R Studio, knitting Rmd documents into HTML files
- Get comfortable with navigating R help files
- Get comfortable with installing R packages


Questions
===
- HiPerGator for student, how should students use it?
- Targeted audience
- computing vs algorithm? Emphasize
- In class lab/ all lectures?

