---
title: "HW example"
author: "Caleb"
date: "Due: 11:59 pm, Sep 3rd, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question A (0 pts)
#### 1. Calculate $\sum_{i=1}^{1000} \frac{1}{i^2}$ (5 pts)

```{r}
## Your code
i <- 1:1000
result_A1 <- sum(1/i^2)

result_A1
```

#### 2. Fibonacci number follows the following recurrence relation:
$F_n = F_{n-1} + F_{n-2}$.
Given the seed value $F_1 = 1$ and $F_2 = 1$, what is $F_{100}$? (5 pts)

```{r}
## Your code
N <- 100
F <- rep(NA, N)
F[1] <- 1
F[2] <- 1
for(n in 3:N){
  F[n] <- F[n-1] + F[n-2]
}

F[100]
```

## Question B (0 pts)
#### 1. In R base package, there is cars' data. data(cars), plot speed (x axis) vs dist (y axis).
```{r}
## Your code
plot(x=cars$speed, y = cars$dist, xlab="speed", ylab="dist", main="dist vs speed")
```

## Question C (0 pts)

In R base package, there is mtcars' data. data(mtcars)

#### 1. Fit a linear model: treat mpg as response variable and cyl, disp, hp and drat as predictors. (0 pts)
```{r}
## Your code
lmfit <- lm(mpg ~ cyl + disp + hp + drat, data=mtcars)
```
#### 2. Find the p-value for cyl. (0 pts)
```{r}
## Your code
pvalue <- summary(lmfit)$coefficients["cyl", "Pr(>|t|)"]

pvalue
```


## Note:


### Homework should be uploaded to courseweb:
1. Save your compiled result as html file. Rename the file name as: hw0_lastname_firstname.html.
2. RMD file is not required, only upload the html file to the [e-leaning](https://elearning.ufl.edu) website..
3. This is just an example homework, so 0 pts will be counted to your final grade.


### If you generate a figure, please write appropriate figure title, labels, legend if necessary.

### If your code is not intuitive, please write comments to make the code readible.


